Betting and Belief: Prediction Markets and Attribution of Climate Change

### 2016-04-18 presentation/present.Rmd
presentation, now creating pdf not html

---
title: 'Betting and Belief: Prediction Markets and Attribution of Climate Change'
author: "John J. Nay, Martin Van der Linden, Jonathan Gilligan"
date: "April 5, 2016"
output: slidy_presentation
---

@@

>>>>

---
title: 'Betting and Belief: Prediction Markets and Attribution of Climate Change'
author: "John J. Nay, Martin Van der Linden, Jonathan Gilligan"
date: "April 20, 2016"
output: beamer_presentation
---

@@

## Trader Beliefs

- Both when true data generating process is CO2 and TSI, at model initialization approximately half of traders use true data-generating model to make predictions. 
- Traders using true model do not necessarily make perfectly accurate predictions. 
- Although these traders believe in correct *functional form* of model, they still need to calibrate their model based on limited noisy data.
